\pagebreak

\section{ Grunt }

\begin{tabular}{ll}
  Name & Grunt \\
  Size & medium\\
  Type & Bio, Grunt, Walks\\
  Cost & 2mp\\
  Models & 4\\
  Armor & \\
  Available Model Items & 2 hands, unlimited independent equipment \\
  Available Unit Items & 1 Unit Base weapon \\
\end{tabular}

\ \\
Assault: 2/2/2/2 Die: 6+ Armor Penetration: 2 Damage: d6-2 \\
Assault Deflection:  Die: \\
\indent Any 6 on assult die roll (not assault deflection) count as two success and you get to reroll 3 dice (assault or assault deflection) per 6. Each die may be rerolled a maximum of one time (for each wave of rerolls). A new wave of rerolls starts when you get atleast one 6 in the reolled assault dice.\\ Cunning assault[1 for 3] \\
\ \\

{\bf Unit Special} \\
Forward Position[2], Cannot use ranged weapons
\ \\


\ \\ {\bf Movement orders } \\
(slow) - + - + Chase \\
(slow) Chase + - + - \\



{\bf Damage Tables} \\
\ \\ {\bf Regular damage } \\
1-5: kill 1 model \\
6-8: kill 1 model, roll on psychic damage[d6] \\
9+: destroy unit base \\
\ \\ {\bf Psychic damage } \\
4+: unit base shaken \\


%\inclue{damge}







\pagebreak

\section{ BioEngineered Ork }

\begin{tabular}{ll}
  Name & BioEngineered Ork \\
  Size & Medium\\
  Type & Bio, Infantry, Walks\\
  Cost & 4mp, 2xp, 1cp\\
  Models & 4\\
  Armor & \\
  Available Model Items & 4 hands, unlimited independent equipment \\
  Available Unit Items & 1 Unit Base Weapon \\
\end{tabular}

\ \\
Assault: 3/2/2/2 Die: 6+ Armor Penetration: 2 Damage: d6-2 \\
Assault Deflection: 1/-/-/- Die: 6+\\
\indent Any 6 on assult die roll (not assault deflection) count as two success and you get to reroll 3 dice (assault or assault deflection) per 6. Each die may be rerolled a maximum of one time (for each wave of rerolls). A new wave of rerolls starts when you get atleast one 6 in the reolled assault dice. \\
\ \\

{\bf Unit Special} \\
Take Cover[still][-2], May use multiple ranged weapons without any penalties\\ Poison Resistance 1, Fire Resistance 1, Immunity to Acid
\ \\
\ \\
{\bf Ork Musket } \\
\ \\
Angle: */*/-/- Range: 3 Armor Penetration: 2 Damage d6-1 \\
\indent  \\



\ \\
{\bf Ork Musket } \\
\ \\
Angle: */*/-/- Range: 3 Armor Penetration: 2 Damage d6-1 \\
\indent  \\





\ \\ {\bf Fire Orders } \\
(still) - + Fire \\
(still) Fire + -  \\
(still) - + Load \\
(still) Load + - \\
(all) - + Aim \\
(still) Aim + -  \\
\ \\ {\bf Movement Orders } \\
(slow) 360$^0$ + F + 360$^0$ \\
(slow) 360$^0$ + 360$^0$ + 360$^0$ \\
(slow) 360$^0$ + B + - \\
(still) 360$^0$ + - + - \\
(still) 360$^0$ + A + F \\
(slow) - + - + chase \\



{\bf Damage Tables} \\
\ \\ {\bf Regular Damage } \\
1: Bleed[4] \\
2-5: Kill 1 model \\
6-8: Kill 1 Model, d6 Psychic damage \\
9: Destroy unit base \\
\ \\ {\bf Psychic Damage } \\
5+: Unit Shaken \\


%\inclue{damge}







\pagebreak

\section{ Warg Rider }

\begin{tabular}{ll}
  Name & Warg Rider \\
  Size & medium\\
  Type & Bio, Cavalry, Elite, Walks\\
  Cost & 2mp, 4xp\\
  Models & 2\\
  Armor & \\
  Available Model Items & 1 hands, unlimited independent equipment \\
  Available Unit Items &  \\
\end{tabular}

\ \\
Assault: 4/4/3/2 Die: 6+ Armor Penetration: 2 Damage: d6-2 \\
Assault Deflection: 2/2/1/1 Die: 6+\\
\indent Any 6 on assult die roll (not assault deflection) count as two success and you get to reroll 3 dice (assault or assault deflection) per 6. Each die may be rerolled a maximum of one time (for each wave of rerolls). A new wave of rerolls starts when you get atleast one 6 in the reolled assault dice.\\ cunning assault[1 for 4] \\
\ \\

{\bf Unit Special} \\
Fire orders only available if given ranged weapons
\ \\


\ \\ {\bf Movement orders } \\
(fast): 360$^0$ + F + F \\
(fast): F + 360$^0$ + F \\
(fast): F + F + 360$^0$ \\
(fast): F + B + 360$^0$ \\
(fast): - + - + chase \\
(slow): 360$^0$ + 360$^0$ + 360$^0$ \\
(slow): 360$^0$ + F + 360$^0$ \\
(slow): - + - + chase \\
(slow): 360$^0$ + A + F \\
\ \\ {\bf Fire Orders } \\
Load + - \\
fire + - \\
- + fire \\



{\bf Damage Tables} \\
\ \\ {\bf Psychic Damage } \\
5+: unit shaken \\
\ \\ {\bf Regular Damage } \\
2-3: Bleeding[6] \\
4-6: Bleeding[6], +1 to future damage, psychic damage[d6] \\
7+: kill 1 model, psychic damage[d6] \\


%\inclue{damge}







\pagebreak

\section{ Speedhead }

\begin{tabular}{ll}
  Name & Speedhead \\
  Size & Medium\\
  Type & Mechanical, Bio Crew, Vehicle, Track\\
  Cost & 6ip\\
  Models & 1\\
  Armor & 8/7/7/7\\
  Available Model Items &  \\
  Available Unit Items &  \\
\end{tabular}

\ \\
Assault: 8/6/4/4 Die: 6+ Armor Penetration: 3 Damage: d8 \\
Assault Deflection: 2/1/-/- Die: 6+\\
\indent Drive Past[4+]: Works as pre-assault retreat, except you may {\it retreat} in the hex directely ahead. Note that is can only be attempted if the hex directly ahead neither becomes overcrowded, is an illegal hex or contain enemies. \\ For each 6 you roll in regular assault, reroll up too 1 dice from initial assault die pool (assault or assault deflection), rerolling each die a maximum of 1 times (for each wave of rerolls, gaining a new wave for every wave you get a 6). A new wave of rerolls starts when you get atleast one 6 in the reolled dice. \\ When moving fast, unit gains Fear[6] \\
\ \\

{\bf Unit Special} \\
Flamethrower: may allways be fired in any shooting step as long as you still have ammo left. Do not need an order to do so \\ Fire and load both rear guns (Speed Cannon and Shriek) simultatniously, and track ammo simultaniously. All targets of both weapons must be within the same angle, but not neccesarily same target.
\ \\
\ \\
{\bf Flamethrower } \\
\ \\
Angle: */-/-/- Range: 1 Armor Penetration: 3 Damage d8 fire damage + d4 crew damage \\
\indent Fire at all hexes possible simultaniously: Area(3+) at point blank range, Area(4+) in the hex at long range directly ahead, and Area(5+) for the two hexes which is on long range and on edge of firing arc. \\ Any target unit effected atleast once is set on FIRE. Fireresistance reduces base damage and crew damage from this weapon. \\ Limited Ammo: May be fired a maximum of 3 times. \\ Starts the game with all 3 ammo loaded \\



\ \\
{\bf Speed Cannon } \\
\ \\
Angle: -/-/*/* Range: 2 Armor Penetration: 6 Damage d6+1 \\
\indent Burst(5): Requires 5 ammo to be shot, but each time it is shot, it fires 5 times \\



\ \\
{\bf Shriek } \\
\ \\
Angle: -/-/*/* Range: 2 Armor Penetration: 2 Damage d4-2+ d6 psychic damage \\
\indent Burst(5) Must have loaded 5 ammo to be fired, but each time it is fired, it's fired 5 times \\





\ \\ {\bf Movement } \\
(slow) L + F + L \\
(slow) R + F + R \\
(slow) F + - + - \\
(default Slow) - + - + B \\
(default still) - + - + A \\
(slow) A + F + F \\
(fast) F + F + F \\
(fast) L + F + F \\
(fast) R + F + F \\
(fast) F + F + L \\
(fast) F + F + R \\
(default fast) - + B + B \\
(fast) B + L + F \\
(fast) B + R + F \\
(fast) B + F + - \\
\ \\ {\bf Fire Orders } \\
(all) Load + Load \\
(all) Load + Fire Burst(5) \\
(all) Fire Burst(5) + Load \\



{\bf Damage Tables} \\
\ \\ {\bf Regular Damage } \\
1-4: Light damage[d6] \\
5-8: Critical Damage[d6], +1 on future damage \\
9+: unit destroied \\
\ \\ {\bf Light Damage } \\
1-4: +1 on future damage \\
5-6: Unit Shaken \\
\ \\ {\bf Critical Damage  } \\
1-3: x3 light damage[d6] \\
4: Cannot rotate \\
5: -1 to hit, +1 to be hit (ranged and assault) \\
6: Unit set on fire \\
\ \\ {\bf Crew Damage } \\
4-5: Misfire[2-] \\
6-7: as -45, shaken \\
8-11: as 6-7, +3 to future crew damage \\
12: Unit destroied \\


%\inclue{damge}







\pagebreak\section{ Clockwork Monocular }

\begin{tabular}{ll}
    Cost & 1cp \\
    Required & Unit Base: Infantry\\
    Type & Infantry, indepenent equipment\\
\end{tabular}
\ \\
Reroll 2 dice in ranged combat per natural 6 rolled for to-hit (regardless of wether that was a hit or not). Each die may be rerolled a maximum of one time (for each wave of rerolls). A new wave of rerolls starts when you get atleast one 6 in the reolled dice. \\

\ \\

{\bf Orders Gained}
['']

{\bf Orders Lost}
['']
\section{ Clockwork Shield }

\begin{tabular}{ll}
    Cost & 2cp \\
    Required & Unit Base: Infantry or Grunt\\
    Type & Infantry, 1handed weapon\\
\end{tabular}
\ \\
Assault Modification: unmodified Assault AP:  Assault Damage: unmodified\\
Assault Deflection Modification: +1/-/-/-, Deflection die: 6+ \\


Unit base gains damage resistance 1\\ Multipe shields: Damage resistance is NOT cumulative, but the assault deflection is. Thus, you may have two shield on same model if you wish. However the model is equiped with nothing but shields it gains -1/-1/-1/-1 penalty on assault values. (thus 2 shields is only sensable you have 4 arms)

{\bf Orders Gained}
['']

{\bf Orders Lost}
['']
\section{ Flame-covered-axe }

\begin{tabular}{ll}
    Cost & 2cp \\
    Required & Model: Elite Infantry or Elite Cavalry\\
    Type & Infantry, 1handed weapon\\
\end{tabular}
\ \\
Assault Modification: unmodified Assault AP:  Assault Damage: d6+1 + d4 crew damage\\
Assault Deflection Modification: -, Deflection die: n.a \\
Fire, Minor Acid[1 for 2], Poison[4][1 for 2]



{\bf Orders Gained}
['']

{\bf Orders Lost}
['']
\section{ Ork Pistol }

\begin{tabular}{ll}
    Cost & 1cp \\
    Required & Unit Base: Infantry or Cavalry\\
    Type & Infantry, 1handed weapon\\
\end{tabular}
\ \\
\indent Angle: */*/*/* Range: 3  AP: 2 Damage d6-1 \\
1 handed weapon. Infantry may combine pistol with another 1-handed weapon. \\ If combined with another pistol, you may load and fire both pistol simultaniously, but with an extra -1 to hit penalty.
\ \\

{\bf Orders Gained}
['(still) Load(2) + -', '(still) - + Load(2)', '(still, slow) fire + -', '(still, slow) - + fire']

{\bf Orders Lost}
['']
