\pagebreak

\section{ Elf Infantry }

\begin{tabular}{ll}
  Name & Elf Infantry \\
  Size & Medium\\
  Type & Bio, Infantry, Walks\\
  Cost & 6mp\\
  Models & 4\\
  Armor & \\
  Available Model Items & 2 hands, unlimited independent equipment \\
  Available Unit Items & 1 Unit Base Weapon \\
\end{tabular}

\ \\
Assault: 1/1/1/1 Die: 5+ Armor Penetration: 2 Damage: d6-2 \\
Assault Deflection:  Die: \\
\indent Cunning Assault[1 for 2], Pre-Assualt retreat[5+] \\
\ \\

{\bf Unit Special} \\
Take Cover[still][-2]
\ \\
\ \\
{\bf Rifle } \\
\ \\
Angle: */*/*/* Range: 5 Armor Penetration: 2 Damage d6-2 \\
\indent  \\





\ \\ {\bf Movement Orders } \\
(slow) 360$^0$ + F + 360$^0$ \\
(slow) 360$^0$ + 360$^0$ + 360$^0$ \\
(slow) 360$^0$ + B + - \\
(still) 360$^0$ + - + - \\
(still) 360$^0$ + A + F \\
(slow) 360$^0$,A + F + F \\
(fast) 360$^0$ + F + B[rest] \\
(rest) - + - + A(slow) \\
(rest) - + - + A(still) \\
(still) 360$^0$,A,A + F + F \\
(default slow) - + - +flee \\
(default fast) - +flee + B[rest] \\
(default rest) - + - + - \\
(default still) - + A + flee \\
\ \\ {\bf Fire Orders } \\
(still only) - + Fire \\
(still only) Fire + -  \\
(still only) - + Load \\
(still only) Load + - \\
(still only) - + aim \\
(still only) aim + -  \\



{\bf Damage Tables} \\
\ \\ {\bf Regular (fire, poison) damage } \\
0-6: kill 1 model\\ half + to future damage rounded down. \\ If killed by poison/bleeding, remove that instance \\
7-8: kill 1 model, psychic damage[d6]\\ half + to future damage rounded down. \\If killed by poison/bleeding, remove that instance \\
9: kill all 4 \\
\ \\ {\bf Psychic damage } \\
4+ shaken \\


%\inclue{damge}







\pagebreak

\section{ Illusion }

\begin{tabular}{ll}
  Name & Illusion \\
  Size & Medium\\
  Type & Illusion\\
  Cost & 2cp\\
  Models & 4\\
  Armor & \\
  Available Model Items &  \\
  Available Unit Items &  \\
\end{tabular}

\ \\
Assault: 1/-/-/- Die:  Armor Penetration: N.A. Damage: d6 Psycic Damage \\
Assault Deflection: - Die: 5+\\
\indent  \\
\ \\

{\bf Unit Special} \\
When fired at, you may pretend to look at normal infantry damage table unless the damage is 4 or above, for which the illusion is given away and is removed from play. \\ Further, if the illusion is matched with one real infantry base, it may mimic the orders of that infantry, and may follow it where ever the infantry goes. \\ The illusion have the exact same modifiers and abilities with regard to being hit as the infantry it is mimicing. Thus, the illusion has Take Cover[still][-2], Take Cover[still][-3], and camufloulage[forrest][-1] as appropritate \\ Thus the enemy do not know which are illusions and which are real. However if, for any reason, the enemy gets information which gives the illusion away, the illusion is not removed from play, but must be identified by an illusion marker. For example if the illusion was fired at by something which does psycic damage, it would require you to tell the enemy that this unit does not have a psycic damage table, which would give the illusion away. \\ If the illusion is not in a hex with a friendly infantry, it has only chase order available
\ \\


\ \\ {\bf Movement Orders } \\
- + chase + chase \\



{\bf Damage Tables} \\
\ \\ {\bf Regular (fire) Damage } \\
0-3: Eliminate 1 model\\ half + to future damage rounded down. \\ If killed by poison/bleeding, remove that instance \\
4+: unit base destroyed \\


%\inclue{damge}







\pagebreak

\section{ Bear Rider }

\begin{tabular}{ll}
  Name & Bear Rider \\
  Size & Medium\\
  Type & Bio, Cavalry, Walks\\
  Cost & 2mp, 6xp\\
  Models & 1\\
  Armor & 7/6/6/6\\
  Available Model Items &  \\
  Available Unit Items &  \\
\end{tabular}

\ \\
Assault: 6/4/2/1 Die: 5+ Armor Penetration: 2 Damage: d6+1 \\
Assault Deflection: 1/-/-/- Die: 5+\\
\indent Cunning Assault[1 for 3] \\
\ \\

{\bf Unit Special} \\
Poison Resistance 2
\ \\
\ \\
{\bf GattlingGun } \\
\ \\
Angle: */*/*/* Range: 2 Armor Penetration: 3 Damage d6-1 \\
\indent Focus Fire[aim]: roll 6 dice at same unit base. \\ If not using aim, fire once at all enemy units within range and within one angle of fire \\ Covered In bullets: if not using aim, a natural 6 on a to-hit die is considered a hit regardless of to-hit modifiers. \\





\ \\ {\bf Fire orders } \\
+ - Load \\
+ - Fire \\
+ - aim \\
\ \\ {\bf Movement } \\
(slow) 360$^0$ + F + 360$^0$ \\
(default slow) - + Flee + 360$^0$ \\
(slow) 360$^0$ + B + 360$^0$ \\
(still) 360$^0$ + A + F \\
(still) 360$^0$ + - + - \\



{\bf Damage Tables} \\
\ \\ {\bf Regular (fire, poison, bleeding) damage } \\
2-6: +1 to future damage, Bleed[4] \\
7-9: +2 to future damage, Bleed[6], psychic damage[d6] \\
10: killed \\
\ \\ {\bf Psychic damage } \\
6+: shaken \\


%\inclue{damge}







\pagebreak

\section{ Tattoo Ink }

\begin{tabular}{ll}
  Name & Tattoo Ink \\
  Size & Medium\\
  Type & Mechanical, Bio Crew, Vehicle, Half-track\\
  Cost & 4ip\\
  Models & 1\\
  Armor & 8/6/6/6\\
  Available Model Items &  \\
  Available Unit Items &  \\
\end{tabular}

\ \\
Assault: 3/2/2/2 Die: 5+ Armor Penetration: 3 Damage: d6-1 \\
Assault Deflection: 2/-/-/- Die: 5+\\
\indent  \\
\ \\

{\bf Unit Special} \\
Gun Blazing: Ignore to-hit penalties for moving fast\\ May fire two SMG (and each SMG fire twice) in addition to Gattle Gun any time a fire order is given.\\ One SMG must fire in same angle as Gattle Gun, the other SMG must fire in the forward direction. However, SMG never gains benefit of aim, only Gattle gun do.\\ Movement: road: if on a road, you may move along a road using this order
\ \\
\ \\
{\bf Gattle Gun } \\
\ \\
Angle: */*/*/* Range: 4 Armor Penetration: 5 Damage d6 \\
\indent May load up to 5 shots. \\



\ \\
{\bf SMG } \\
\ \\
Angle: */*/*/* Range: 3 Armor Penetration: 1 Damage d6-3 \\
\indent Always treated as loaded, and may fire 2 shots per fire order (per model) \\





\ \\ {\bf Fire } \\
(still) Fire + aim \\
(still) aim + Fire \\
(all) Fire + Fire  \\
(still) Load + aim \\
(still, slow) Load + Load \\
\ \\ {\bf Movement } \\
(fast) F+ F + - \\
(fast) F + R + - \\
(fast) F + L + - \\
(fast) F + B + - \\
(fast) B + B + - \\
(default fast) - + B + B \\
(slow) L + - + - \\
(slow) L + L + - \\
(slow) R + - + - \\
(slow) R + R + - \\
(slow) A + F + - \\
(slow) B + - + - \\
(default slow) - + - + B \\
(slow) F + - + - \\
(slow) B + rev + - \\
(still) L + - + - \\
(still) L + L + - \\
(still) L + L + L \\
(still) R + - + - \\
(still) R + R + - \\
(still) R + R + R \\
(still) - + - + - \\
(still) R + A + F \\
(still) L + A + F \\
(still) A + F + - \\
(still) rev + - + - \\
(default still) - + - + - \\
(fast) R+ F + - \\
(fast) L+ F + - \\
(fast) road + road + road \\



{\bf Damage Tables} \\
\ \\ {\bf Critical Damage } \\
1: Shaken \\
2: -1 to hit, +1 to be hit \\
3: Cannot rotate \\
4: Roll 3 times on light damage table \\
5: Treat all B and A orders as illegal. Replace with - \\
6: Fire! \\
\ \\ {\bf Light Damage } \\
1-4: +1 on future damage \\
5-6: shaken \\
\ \\ {\bf Regular (fire) Damage } \\
1-4: Light Damage[d6] \\
5-7: d6 Critical Damage, +1 on future damage \\
8+ Destroyed \\
\ \\ {\bf Crew Damage } \\
3: Misfire[1-] \\
4-5: replace any effect of Misfire[1-] with Misfire[3-] \\
6-7: as 4-5, shaken \\
8-9: as 6-7, +3 to future crew damage \\
10: Crew Killed, Unit Destroyed \\


%\inclue{damge}







\pagebreak\section{ Camuflouflage }

\begin{tabular}{ll}
    Cost & 2cp, 2xp \\
    Required & Unit Base: Infantry\\
    Type & Infantery, Independent Equipment\\
\end{tabular}
\ \\
Unit base gains camuflouflage[forrest][-1] \\

\ \\

{\bf Orders Gained}
['']

{\bf Orders Lost}
['']
\section{ Enhanced Rifle }

\begin{tabular}{ll}
    Cost & 2cp \\
    Required & Unit Base: Infantry\\
    Type & Infantry, 2handed weapon\\
\end{tabular}
\ \\
\indent Angle: */*/*/* Range: 6  AP: 2 Damage d6-2 \\
Unit gain +1 to hit (but only for this weapon)
\ \\

{\bf Orders Gained}
['']

{\bf Orders Lost}
['']
\section{ SMG }

\begin{tabular}{ll}
    Cost & 2cp \\
    Required & Unit Base: Infantry or Elk Cavalery or Eagle Rider\\
    Type & Infantry, 1handed weapon\\
\end{tabular}
\ \\
\indent Angle: */*/*/* Range: 3  AP: 1 Damage d6-3 \\
Always treated as loaded, and may fire 2 shots per fire order (per model)
\ \\

{\bf Orders Gained}
['(all) Fire(smg) + Fire(smg)']

{\bf Orders Lost}
['aim + -', '- + aim']
\section{ Small grenade }

\begin{tabular}{ll}
    Cost & 2cp \\
    Required & Unit Base: Infantry\\
    Type & Infantry, Independent Equipment\\
\end{tabular}
\ \\
\indent Angle: */*/*/* Range: 1  AP: 5 Damage d8 \\
Area(5+) if used by a unit with 1-2 alive models, Area(4+) if used by a unit with 3-4 alive models. May only target units within normal range. limited ammo(3)
\ \\

{\bf Orders Gained}
['(still, slow, fast) - + throw grenade']

{\bf Orders Lost}
['']
