\clearpage

\section{ Abomination Infantry 1 }

\begin{tabular}{ll}
  Name & Abomination Infantry \\
  Size & medium\\
  Models & 4 x Abomination Infantry\\
  Armor & 0\\
  Victory points & 12\\
  Shaken & Movement set to slow. Movement order: [-,-,flee]. May not fire weapons\\
\end{tabular}

Take Cover[still][-2]\\ 
Terror[Range=1][d6]\\ 
Fog: dobble to-hit penalties in smoke/fog and ignore to-hit penalty for enemies in smoke/fog. (however does not ignore line of sight through smoke/fog) hexes. If given additional tentacle weapons, they fire simultainiusly with other weapons on regular Fire order, not Fire(b) order\\ 



{\bf Damage Tables} \\
 {\bf regular } \\
1-6: Kill 1 model \\
7-8: Kill 1 model, psychic damage[d6] \\
9+: Unit destroyed \\
{{\it Note: If one model is killed remove half of the +1 future damage tokens \\ and if killed by bleeding/poison, remove that bleeding/poison token}} \\
 {\bf psychic } \\
4+: shaken \\


\clearpage

\subsection{ Models }

\begin{tabular}{ll}
Model name: & {\bf Abomination Infantry } \\
Type: & [bio, infantry, walks, amphibian] \\
\end{tabular}

Equipment: 1 x Multipurpose Gun, 1 x Fog grenade Mortar \\

Assault: [1, 1, 1, 1] Die: 6+ Armor Penetration: 2 Damage: d6-2 \\
Assault Deflection: [1, 0, 0, 0] Die: 6+\\
\indent +100\% strength and deflections versus shaken units\\ 
Cunning Assault[1 for 2]\\ 
 



{\bf Multipurpose Gun } \\



Range: 5  Angle: [True, True, True, True] AP: n.a Damage: d6 psychic \\
Has two settings. Scare and blow gun. Scare do the regular psychic damage, used by Fire orders. Blow gun is used by Fire(b) orders and only effect shaken bio units. All other units are immune. However, if you manage to cause psycic damage the unit becomes insane in addition to the normal effects of the psycic damage table\\ 




{\bf Fog grenade Mortar } \\



Range: 4  Angle: [True, True, True, True] AP: n.a Damage: n.a \\
Place two smoke tokens in a hex within normal range. Note: choose one hex per model firing this weapon. Uses Ammo as normal. May start the game without ammo, but instead place two smoke tokens in 4 different hexes within range 3 of this unit at start of game (part of setup)\\ 




 















\clearpage

\section{ Horror 1 }

\begin{tabular}{ll}
  Name & Horror \\
  Size & huge\\
  Models & 1 x Horror\\
  Armor & [6, 4, 2, 1]\\
  Victory points & 8\\
  Shaken & Movement set to still. Movement order: [-,-,-]. \\
\end{tabular}

While in fog (in agony phases): Terror[Range=1][d12], Insanity Filed[range=1][d6]\\ 
Insanity Field works like Terror, except it only effects biological units which are already shaken, and if it inflicts any psychic damage, enemy becomes insane in addition to its normal effect\\ 
If horror is either standing in a hex with fog or entering a hex with fog, threat the hex as impassable for enemy chase purposes, forcing them to move into another squar without assault taking place.\\ 
Treat any squares within range 2 of Horror as being a poison cloud[4]\\ 
Immunity to acid and fire, poison resistance 12\\ 
Forward Position[3]\\ 



{\bf Damage Tables} \\
 {\bf regular } \\
1-3: Bleed[6] \\
4-5: As below, +1 to future damage \\
6-8: As below, if caused by bleeding, amplify bleeding \\
9+: Unit destroyed \\
{{\it Note:  Amplify bleeding: Bleed[4] becomes Bleed[6], Bleed[6] becomes Bleed[8] etc up to max Bleed[12]}} \\
{{\it Note: bleeding does not cause more bleeding}} \\
 {\bf psychic } \\
6+: shaken \\


\clearpage

\subsection{ Models }

\begin{tabular}{ll}
Model name: & {\bf Horror } \\
Type: & [bio, monster, walks, amphibian] \\
\end{tabular}

Equipment:  \\

Assault: [6, 4, 4, 2] Die: 4+ Armor Penetration: 2 Damage: d6 \\
Assault Deflection: [2, 0, 0, 0] Die: 4+\\
\indent +100\% strength and deflections versus shaken units\\ 
 



 















\clearpage

\section{ Gigant Frog Riders 1 }

\begin{tabular}{ll}
  Name & Gigant Frog Riders \\
  Size & medium\\
  Models & 2 x Gigant Frog Rider\\
  Armor & 0\\
  Victory points & 10\\
  Shaken & Speed set to slow. Movement order: [-,-,flee]. may not use fire orders\\
\end{tabular}

Poison Resistance 4\\ 
Terror[range=1][d8]\\ 
Fog: dobble to-hit penalties in smoke/fog and ignore to-hit penalty for enemies in smoke/fog. (however does not ignore line of sight through smoke/fog hexes)\\ 



{\bf Damage Tables} \\
 {\bf regular } \\
2-3: bleed[4] \\
4+: kill 1 model \\
{{\it Note: If one model is killed remove half of the +1 future damage tokens \\ and if killed by bleeding/poison, remove that bleeding/poison token}} \\
 {\bf psychic } \\
6+: shaken \\


\clearpage

\subsection{ Models }

\begin{tabular}{ll}
Model name: & {\bf Gigant Frog Rider } \\
Type: & [bio, cavalry, walks, amphibian, frog] \\
\end{tabular}

Equipment: 1 x Frog spit, 1 x Mechanical Melee Contraption, 1 x Frog Cavalry Armor, 1 x Tentacle CracleSpears \\

Assault: [5, 1, 1, 1] Die: 6+ Armor Penetration: 2 Damage: d6 \\
Assault Deflection: [5, 0, 0, 0] Die: 6+\\
\indent Cunning Assault[1 for 3]\\ 
+100\% strength and deflections versus shaken units\\ 
If assault in a hex with fog (smoke token), each hit by this model does an d6 psycic damage in addition to the regular damage. This ability does not stack with more spears.\\ 
poison[4]\\ 
 



{\bf Frog spit } \\



Range: 1  Angle: [True, True, False, False] AP: n.a Damage: n.a \\
Poison[4]\\ 
Always treated as loaded, and fire in both first and second gunnery phase independent of other weapons\\ 




{\bf Mechanical Melee Contraption } \\

Improves assault if ammo is spend. You may spend one ammo in an assault, to increase the success of both assault strength and deflection to 4+ instead of 6+\\ 





{\bf Frog Cavalry Armor } \\

Unit gain [4, 3, 3, 0] in armor.\\ 





{\bf Tentacle CracleSpears } \\






 















\clearpage

\section{ Squ 1 }

\begin{tabular}{ll}
  Name & Squ \\
  Size & lagre\\
  Models & 1 x Squ\\
  Armor & [8, 6, 5, 4]\\
  Victory points & 18\\
  Shaken & Speed set to still, move order: [- - -]. May not fire weapons\\
\end{tabular}

Fog: dobble to-hit penalties in smoke/fog and ignore to-hit penalty for enemies in smoke/fog. (however does not ignore line of sight through smoke/fog hexes)\\ 



{\bf Damage Tables} \\
 {\bf regular } \\
1-3: +1 to future damage \\
4: as below, shaken \\
5-8: as below, d6 critical damage \\
9: Unit destroyed \\
 {\bf critical } \\
1-2: +3 to future damage \\
3: +1 to be hit, -1 to hit \\
4: Cannot rotate \\
5: Unit cannot Move  \\
6: set on fire \\
 {\bf crew } \\
4-5: Crippled Crew, if aleady shaken double initial crew damage \\
6-7: as 4-5, shaken \\
8-11: as 6-7, +3 to future crew damage \\
12: Unit destroyed \\


\clearpage

\subsection{ Models }

\begin{tabular}{ll}
Model name: & {\bf Squ } \\
Type: & [vehicle, mechanical, track, biological crew] \\
\end{tabular}

Equipment: 1 x Confution Gas launcher \\

Assault: [12, 1, 1, 1] Die: 6+ Armor Penetration: 2 Damage: d6-2 \\
Assault Deflection: [6, 0, 0, 0] Die: 6+\\
\indent +100\% strength and deflections versus shaken units\\ 
 



{\bf Confution Gas launcher } \\



Range: 4  Angle: [True, True, False, False] AP: n.a Damage: d6 psychic + d4 crew damage \\
Fires 3 shot per fire order. Each hit gives one confution token to any unit with bio or a bio crew. (se general rules)\\ 




 















