\clearpage

\section{ Transport Zeppelin 1 }

\begin{tabular}{ll}
  Name & Transport Zeppelin \\
  Size & medium\\
  Models & 1 x Transport Zeppelin\\
  Armor & [6, 5, 0, 0]\\
  Victory points & 4\\
  Shaken & Movment set to fast flying. Movement order: [-,F,F].\\
\end{tabular}

May transport up to 2 unit of Infantry or SteamPowerArmor. Unload in any movement phase. When unloading they use hanggliders and are placed up to two hexes in any direction from the transport zeppelin end hex in that movement phase. They may enter assault as part of unloading. Place all infanteri in slow after unloading and treat any movement order up to this point as -\\ 
May not transport any infantri with wheeled shieldwall\\ 



{\bf Damage Tables} \\
 {\bf regular } \\
1-4: +1 on future damage \\
5-8:as below, d6-2 damage to each unit transported by this unit. \\
9: unit and all transported units killed \\


\clearpage

\subsection{ Models }

\begin{tabular}{ll}
Model name: & {\bf Transport Zeppelin } \\
Type: & [zeppelin, flying] \\
\end{tabular}

Equipment:  \\

Assault: [2, 1, 1, 1] Die: 4+ Armor Penetration: 2 Damage: d6-2 \\
Assault Deflection: [0, 0, 0, 0] Die: n.a\\
\indent May not assault ground units\\ 
 



 















\clearpage

\section{ Blast Stick Infantry }

\begin{tabular}{ll}
  Name & Dwarf Infantry \\
  Size & medium\\
  Models & 4 x Dwarf Elite Infantry\\
  Armor & [0, 0, 0, 0]\\
  Victory points & 13\\
  Shaken & Movement set to slow. Movement order: [-,-,flee]. May not fire weapons\\
\end{tabular}

Posion Resistance 2, Fire Resistance 1\\ 
Take Cover[still][-2]\\ 



{\bf Damage Tables} \\
 {\bf regular } \\
1-5: Kill 1 model \\
6-9: Kill 1 model, roll d6 psychic damage \\
10+: Unit killed \\
 {\bf psychic } \\
4+: Unit shaken \\


\clearpage

\subsection{ Models }

\begin{tabular}{ll}
Model name: & {\bf Dwarf Elite Infantry } \\
Type: & [elite, infantry, walks, bio] \\
\end{tabular}

Equipment: 1 x Blast Sticks, 1 x Vest of Life Support, 1 x Trench Coat of Resistance, 1 x Industrial Small Arms production \\

Assault: [2, 2, 1, 1] Die: 4+ Armor Penetration: 5 Damage: d6+1 \\
Assault Deflection: [2, 1, 1, 1] Die: 4+\\
\indent cunning assault[1 for 2]\\ 
Cunning Assault[1 for 1]\\ 
Cunning Assault[1 for 1]\\ 
Cunning Assault[1 for 1]\\ 
Cunning Assault[1 for 1]\\ 
Cunning Assault[1 for 1]\\ 
Cunning Assault[1 for 1]\\ 
 

good shot: +1 to hit\\ 
unit gains psycic resistance 2 as long as 1 elite model is alive\\ 


{\bf Blast Sticks } \\






{\bf Vest of Life Support } \\

Unit gains 1 endurence token per regular model  and 2 endurence tokens per elite model in the unit. See general rules for effect\\ 





{\bf Trench Coat of Resistance } \\

Unit improves poison resistance and fire reistance with 1\\ 
Unit gains imunity to minor acid\\ 





{\bf Industrial Small Arms production } \\






 















\clearpage

\section{ GunBlasterWagon 1 }

\begin{tabular}{ll}
  Name & GunBlasterWagon \\
  Size & Large\\
  Models & 1 x GunBlasterWagon\\
  Armor & [8, 10, 10, 7]\\
  Victory points & 18\\
  Shaken & Movment set to still. Movement order: [-,-,-]. May not fire weapons\\
\end{tabular}

Fire Resistance 2\\ 
optimal Point blank: +1 to hit at point blank range\\ 
Perfect Breaking: After 3rd movement step, it may apply an B or B+B in addition to it's normal action. This may be applied regardless of what the movement order at step 3 is.\\ 



{\bf Damage Tables} \\
 {\bf critical } \\
1: -1 to-hit, +1 to-be-hit \\
2: Cannot Rotate \\
3: Cannot Move \\
4-5: +3 to future damage \\
6: set on Fire \\
 {\bf regular } \\
1-3: +1 to future damge \\
4: as below, shaken \\
5-8: as below, Critical damage[d6] \\
9+: Destroyed \\
 {\bf crew } \\
4-5: Crippled Crew, if aleady shaken double initial crew damage \\
6-7: as 4-5, shaken \\
8-12: as 6-7, +3 to future crew damage \\
13: Unit destroyed \\


\clearpage

\subsection{ Models }

\begin{tabular}{ll}
Model name: & {\bf GunBlasterWagon } \\
Type: & [mechanical, bio crew, track, vehicle] \\
\end{tabular}

Equipment: 1 x Broadside Guns \\

Assault: [2, 2, 2, 2] Die: 4+ Armor Penetration: 3 Damage: d6-2 \\
Assault Deflection: [2, 0, 0, 0] Die: 4+\\
\indent  



{\bf Broadside Guns } \\



Range: 3  Angle: ['0', 'x2', 'x2', '0'] AP: 7 Damage: d6+2 \\
Must be loaded with 2 ammo before these guns can be fired. Can have 2 ammo stored at any given time. Each time it is loaded it is loaded with 1 ammo, thus you need to spend 2 reloading actions before it can fire again\\ 
After firng these weapon, place a Poison Cloud[4] at point blank range from any of the directions that fired.\\ 




 















